Implementing DNS in C0

### 2017-11-17 proposal.tex
fix a few typos

\begin{lstlisting}
int parse_domain_name(int cursor, int[] msg, domain_name_t dest);
int parse_resource_record(int cursor, int[] msg, resource_record_t dest);
int parse_header(int cursor, int[] msg, header_t dest);
\end{lstlisting}

@@

\begin{lstlisting}
int parse_domain_name(int cursor, int[] data, domain_name* dest) {
  int* len = alloc(int);

>>>>

\begin{lstlisting}
int parse_domain_name(int cursor, int[] msg, domain_name_t* dest);
int parse_resource_record(int cursor, int[] msg, resource_record_t dest);
int parse_header(int cursor, int[] msg, header_t dest);
\end{lstlisting}

@@

\begin{lstlisting}
int parse_domain_name(int cursor, int[] data, domain_name_t* dest) {
  int* len = alloc(int);
